Kung Faux Pandas \\ \large A tool for enabling data sharing in health care

### 2018-05-18 paper/main.tex

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

@@

@@

The unique contribution to the space of reproducible machine learning by this paper is a no-configuration required method for faux data creation from user generated queries. The faux data will resemble the original data set but can be used freely without compliance risk because it contains no Protected Health Information (PHI). Furthermore, with this method it is possible for an investigator to perform hypothesis articulation, data cleaning, analysis, visualization, and documentation without the ever having access to the underlying PHI data.

@@

Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability. Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}; others such as Drummond use the terms in a reverse fashion \cite{drummond_replicability_2009}. Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment. One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducibility as having: data, input parameters, documentation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by paper \cite{schwab_making_2000}. Reproducibility should be treated as a minimum required standard that all published research should meet \cite{peng_reproducible_2006}. Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration and run times, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly. The last item is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article. Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage[super]{nth}     % JK: for 1st-ing and 2nd-ing

@@

\makeatletter

\newenvironment{chapquote}[2][2em]
  {\setlength{\@tempdima}{#1}%
   \def\chapquote@author{#2}%
   \parshape 1 \@tempdima \dimexpr\textwidth-2\@tempdima\relax%
   \itshape}
  {\par\normalfont\hfill--\ \chapquote@author\hspace*{\@tempdima}\par\bigskip}
\makeatother

@@

The unique contribution to the space of reproducible machine learning by this paper is a no-configuration required method for faux-data creation from user generated queries. The faux-data will resemble the original data set but can be used freely without compliance risk because it contains no Protected Health Information (PHI). Furthermore, with this method it is possible for an investigator to perform hypothesis articulation, data cleaning, analysis, visualization, and documentation without the ever having access to the underlying PHI data.

@@

\begin{chapquote}{Richard Dawkins on his preference for the scientific method over other modes of inquiry.}
``Because it works, bitches.''
\end{chapquote}

The ability of independent investigators to verify results is perhaps \emph{the} most fundamental feature that separates science from other forms intellectual inquiry.  Unfortunately, the mechanisms of populating the scientific literature were designed on \nth{17} century assumptions which are inadequate for some modern scientific endeavors such as machine learning.

Though there are semantic variations in the use of the words "replicate," "reproduce," etc., most commentaries on the subject agree that an independent experiment with confirmatory results is the strongest support of any experiment \cite{leek_opinion_2015, drummond_replicability_2009}.  In the machine learning context, the ability to independently arrive at similar results from similar data requires the documentation of many technical (and frankly, banal) parameters which is rarely done within published papers.  Many of these, such as the versions used of various software libraries, can be captured in virtual environments, but parameters related to the data are often much trickier to capture, particularly if the data used in an analysis is sensitive and cannot be shared.

\subsection{Seth's Original}
Over the past 18 years, there has been several significant papers clarifying the definition and importance of reproducibility along with the closely related term replicability. Leek and Peng have defined reproducibility as the "ability to recompute data analytic results given an observed dataset and knowledge of the data analysis pipeline," and replicability as "the chance that an independent experiment targeting the same scientific question will produce a consistent result" \cite{leek_opinion_2015}; others such as Drummond use the terms in a reverse fashion \cite{drummond_replicability_2009}. Despite the semantic disagreement, both groups agree that an independent experiment with confirmatory results is the strongest support of any experiment. One early influential paper on the topic of reproducibility in scientific computing details key factors in reproducibility as having: data, input parameters, documentation, software code, and an environment capable of running the provided software code; items that cannot easily nor clearly be communicated by paper \cite{schwab_making_2000}. Reproducibility should be treated as a minimum required standard that all published research should meet \cite{peng_reproducible_2006}. Specifically in the context of machine learning, this means including details to a level someone else could create the same environment including hardware configuration and run times, data used for all experiments, source code, documentation on data and how to run/configure software, and tests that verify the software runs correctly. The last item is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article. Once a result can be reproduced, new researchers can then build upon the methods, gather new data for testing/validation, or discover alternative methods to replicate a result.
